Prehensile Manipulation Planning: Modelling, Algorithms and Implementation

### 2020-10-14 hpp.tex
Write conclusion and set doublespace mode.

>>>>

\section{Conclusion and future work}

This paper presents a software platform aimed at prototyping and solving
prehensile manipulation planning problems. The platform provide an original
algorithm M-RRT that is an extension of RRT exploring the leaves of the
foliation defined by the manipulation constraints. The automatic insertion
of way point states make the resolution more efficient and the resulting paths
more natural.

We think that this platform is a perfect basis for researchers who want to
develop and benchmark new manpulation planning algorithms.

To show the maturity of the project, we provide a docker image embarking the
software.

As a future work, we aim at working on general manipulation planning algorithms
that can handle use cases as diverse as those proposed in the benchmark section.
A good candidate is a generalization of RMR*~\cite{schmitt17icra}. We also aim at working on manipulation path optimization since paths computed by
random algorithms are too long to be applied on real robots as such.
